Impact of switching bug trackers: a case study on a medium-sized open source project

### 2019-03-31 article/article.tex
Functional notebook with OCaml for extended version.

The impact of the bug reporting environment on the bug tracking activity is difficult to assess because of the lack of comparison points. In this paper, we take advantage of the switch, from Bugzilla to GitHub, of the bug tracker of Coq, a medium-sized open source project, to evaluate the impact that such a change can have.

We first report on the switch itself, in particular the migration of 4900 preexisting bug reports using the GitHub issue import API. Then we analyze data from before and after the switch using a Regression on Discontinuity analysis, a novel methodology in the context of empirical software engineering.
We show that the switch induces an increase in bug reporting, particularly from principal developers themselves, and more generally an increased engagement with the bug tracking platform, with more comments by developers and also more external commentators.
\end{abstract}

@@

\begin{IEEEkeywords}
bug tracker, switch, migration, bug report, issue, GitHub, Bugzilla, open source, data mining, Regression on Discontinuity
\end{IEEEkeywords}
%
%
%
\section{Introduction}

@@

\subsection{Cumulative number of bug reports and bug comments}

Fig.~\ref{cumulative_bugs} and~\ref{cumulative_comments} give a first (cumulative) view of two of our outcome variables: the number of bug reports, and the number of comments. From these figures, we can clearly notice the dominance of developers in the number of bug comments and the dominance of non-developers in the number of bug reports. We can also already notice some slope changes at the bug tracker switch date. The magnitude and significance of this changes will be assessed in Sec. \ref{results}.

\begin{figure}
\includegraphics{cumulative_bugs.eps}
\caption{Cumulative number of bug reports (since 2008).} \label{cumulative_bugs}
\end{figure}

\begin{figure}
\includegraphics{cumulative_comments.eps}
\caption{Cumulative number of comments (since 2008).} \label{cumulative_comments}
\end{figure}

@@

>>>>

The impact of the bug reporting environment on the bug tracking activity is difficult to assess because of the lack of comparison points. In this paper, we take advantage of the switch, from Bugzilla to GitHub, of the bug tracker of Coq, a medium-sized open source project, to evaluate and interpret the impact that such a change can have.

We first report on the switch itself, including the migration of preexisting bug reports. Then we analyze data from before and after the switch using a Regression on Discontinuity analysis, a novel methodology in the context of empirical software engineering. We complete this quantitative analysis with qualitative data from interviews with developers.
We show that the switch induces an increase in bug reporting, particularly from principal developers themselves, and more generally an increased engagement with the bug tracking platform, with more comments by developers and also more external commentators.
\end{abstract}

@@

\begin{IEEEkeywords}
bug tracker, switch, migration, bug report, issue, GitHub, Bugzilla, open source, data mining, Regression on Discontinuity, interviews
\end{IEEEkeywords}
%
%
%
\section{Introduction}

@@

%\subsection{Cumulative number of bug reports and bug comments}

%Fig.~\ref{cumulative_bugs} and~\ref{cumulative_comments} give a first (cumulative) view of two of our outcome variables: the number of bug reports, and the number of comments. From these figures, we can clearly notice the dominance of developers in the number of bug comments and the dominance of non-developers in the number of bug reports. We can also already notice some slope changes at the bug tracker switch date. The magnitude and significance of this changes will be assessed in Sec. \ref{results}.

%\begin{figure}
%\includegraphics{cumulative_bugs.eps}
%\caption{Cumulative number of bug reports (since 2008).} \label{cumulative_bugs}
%\end{figure}

%\begin{figure}
%\includegraphics{cumulative_comments.eps}
%\caption{Cumulative number of comments (since 2008).} \label{cumulative_comments}
%\end{figure}

@@

\begin{figure}
\includegraphics{reporters_with_releases.eps}
\caption{Average number of weekly distinct reporters by 4-week period with release dates (since 2008).} \label{reporters_with_releases}
\end{figure}

\begin{figure}
\includegraphics{commentators_with_releases.eps}
\caption{Average number of weekly distinct commentators by 4-week period with release dates (since 2008).} \label{commentators_with_releases}
\end{figure}
